Output Summary

### 2020-09-09 03-post-process/output-plots.Rmd
Include plots for fits to data
* abundance data,
* survival data,
* composition data

>>>>

# Fit to Data {.tabset .tabset-pills}

In the figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

## Abundance Data

```{r abundance-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^Pa[.+,1]$"), jags_data$Pa_obs[observable,1], main = "Fall Trap Abundance")
plot_tseries(post_summ(post, "^Mb[.+,2]$"), jags_data$Mb_obs[observable,2], main = "Spring Trap Abundance")
plot_tseries(post_summ(post, "^Ra_tot["), jags_data$Ra_obs[observable], main = "Weir Abundance")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Abundance")
```

## Survival Data

```{r survival-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))

plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "Summer Tagging to LGD")
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "Fall Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2]), main = "Spring Trap to LGD")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

## Composition Data

```{r comp-data-fits, fig.width = 6, fig.height = 5}
# calculate observed q
q_obs = t(apply(jags_data$x_obs, 1, function(y) y/sum(y)))

par(mfcol = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "^q[.+,1]$"), q_obs[observable,1], main = "Female Age 3")
plot_tseries(post_summ(post, "^q[.+,2]$"), q_obs[observable,2], main = "Female Age 4")
plot_tseries(post_summ(post, "^q[.+,3]$"), q_obs[observable,3], main = "Female Age 5")
plot_tseries(post_summ(post, "^q[.+,4]$"), q_obs[observable,4], main = "Male Age 3")
plot_tseries(post_summ(post, "^q[.+,5]$"), q_obs[observable,5], main = "Male Age 4")
plot_tseries(post_summ(post, "^q[.+,6]$"), q_obs[observable,6], main = "Male Age 5")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
```
